FraCaS: Temporal Analysis

### 2020-05-19 paper2020/paper.tex
rework background

\section{Background}
\paragraph{GF}
If needed
\paragraph{Coq}
If needed
\paragraph{Temporal Semantics}
Stergios

@@

\section{Our Compositional Semantics}

Our interpretation is cast withing the framework of a largely standard
montegovian semantics \cite{todo}. In brief, sentences are interpreted as
propositions, verbs and noun-phrases as predicates.  We use
type-raising of noun-phrases, to support quantifiers \cite{PTQ}.

We support additionally various constructinos and phenomena present in
the testsuite, including adjectives, adverbs, nouns, verbs, anaphora,
etc. We direct the reader to our previous work for details \ifanon
(citations anonymized) \else \citet{bernardy_type_2017,bernardy_wide_2019} \fi, but the particular
treatment of such phenomena is largely independent from our treatment
of time.
%
Here we simply ignore these aspects beyond the fact that they
are handled correctly in most of the case of the FraCaS testsuite.  In
particular, non-temporal anaphoroi are resolved as they should be.

@@

\paragraph{(un)repeatable achievements}
The principle of using unicity of action interacts well with the usual
interpretation of quantifiers (and anaphora).  Indeed, using it, we
can refute problem (279), as expected by the testsuite:

@@

\section{Results and evaluation}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy:2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our systems on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.

>>>>

\section{Background}

\paragraph{GF}
We work on a syntactic representation of the FraCaS test suite in GF
abstract syntax~\citep{Ljunglof:2012}. Thus, we skip the
parsing phase and avoid any syntactic ambiguity.

For the purpose of this paper, the important point is that GF the
syntax aims at a balance of sufficient abstraction to provide a
semantically-relevant structure, but at the same time it embeds
sufficiently many syntactic features to be able to reconstruct
unambiguously natural-language text. Example \label{ex:onelingex}
shows an example abstract syntax tree and its realisation in English.

\paragraph{Coq}
If needed

\paragraph{Montegovian semantics}
\todo{integrate to background}

Our interpretation is cast withing the framework of a largely standard
montegovian semantics \cite{todo}. In brief, sentences are interpreted as
propositions, verbs and noun-phrases as predicates.  We use
type-raising of noun-phrases, to support quantifiers~\cite{PTQ}.

We support additionally the basic constructions and phenomena present
in the testsuite, including adjectives, adverbs, nouns, verbs,
anaphora, etc. We direct the reader to our previous work for details
\ifanon (citations anonymized) \else
\citet{bernardy_type_2017} \fi, but the particular
treatment of such phenomena is essentially independent from our
treatment of time:
in this paper we simply ignore these aspects beyond the fact that they
are handled correctly in most of the cases of the FraCaS testsuite.

\paragraph{Dynamic semantics}
We additionally assume support for (non-temporal) anaphora, using a
monadic-based dynamic semantics \cite{TODO}.  Our particular
implementation is not perfect \ifanon (citations anonymized) \else
\citet{ bernardy_wide_2019} \fi but non-temporal anaphoroi in the
testsuite are generally resolved as they should be.

As for other basic phenomena, there is not much interaction between
our treatment of time and non-temporal anaphora. One critical
exception is discussed in \cref{sec:repeatable-achievements}.

\paragraph{Temporal Semantics}
Stergios

@@

@@

\paragraph{(un)repeatable achievements}
\label{sec:repeatable-achievements}
The principle of using unicity of action interacts well with the usual
interpretation of quantifiers (and anaphora).  Indeed, using it, we
can refute problem (279), as expected by the testsuite:

@@

\section{Results and evaluation}
\todo{How this system is new; comparison with other systems; first system that does the whole fracas}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy:2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our systems on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.
